Attribute fusion in a latent process model for time series of graphs

### 2011-05-13 ssp2011.tex
Finish the proof of Eq.(42)

@@

\usepackage{amssymb}

@@

    \rightarrow \infty$ and $u = o(\sqrt{n})$, we have the
    following large deviations result \cite[Theorem~2, \S
    XVI.7]{feller71:_introd_probab_theor_its_applic}.

@@

      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \exp\Bigl(u^2
      h(\tfrac{u}{\sqrt{n}})\Bigr) \Bigl[1 + O(\tfrac{u}{\sqrt{n}}) \Bigr]

@@

    where $h(z)$ is a power series defined by

@@

      z^{2} h(z) = h_0 z^3 + h_1 z^4 + \dots

@@

    and the $h_i$ are constants. Letting $u_n = a_n + b_n x$ in
     1 - F_n(u_n) = (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
     O(\tfrac{u_n^{4}}{n}))
    for some constant $C$. We therefore have

@@

      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n}
      &= \Bigl[\Phi(u_n) + \Phi(u_n) 
      \tilde{O}(\tfrac{1}{\sqrt{n}})\Bigr]^{n} \\
      &= \Bigl[\Phi(u_n) + \tilde{O}(\tfrac{1}{n^{3/2}})\Bigr]^{n} \\
      &= (\Phi(u_n))^{n} + \tilde{O}(\tfrac{1}{n^{1/2}}) \\

@@

    where $\tilde{O}$ denote that the powers of $u_n =
    O(\log{n})$ are ignored. Eq.~\eqref{eq:22} is established and
    we obtain the limiting Gumbel distribution for

@@

  For ease of exposition, we will drop the time index $t =
  t^{*}$ from our notations and discussion. Let

@@

    \limsup \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim

@@

  \liminf \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(

@@

    P_2 & \leq n \sum_{D(v) \geq
        d_{n,m}}{\mathbb{P}\biggl( Y(v) - \mathbb{E}[Y(v)] \geq
        \vartheta_n \biggr) p_{e,f}}

@@

  &= n \sum_{D(v) \geq d_{n,m}}{\mathbb{P}\biggl(
    \tfrac{Y(v) - \mathbb{E}[Y(v)]}{\sqrt{\mathrm{Var}[Y(v)]}} \geq
    \tfrac{\vartheta_n}{\sqrt{\mathrm{Var}[Y(v)]}} \biggr) p_{e,f}} \\
    &\leq n \sum_{D(v) \geq d_{n,m}} (1 + o(1)) \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} \\
    &= o(1)

@@

$\{v \in [m] \cap \mathfrak{E} \cap\mathfrak{F}\}$ and $\{v \in [m]

@@

  We first show $\mathbb{P}( \cup_{v

@@

      N_{\kappa}) = o(1)$. 

@@

\end{proof}
\bibliography{ssp2011}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\usepackage[utopia]{mathdesign}

@@

%\usepackage{amssymb}

@@

    \rightarrow \infty$ and $u = O(\log{n})$, we have the
    following moderate deviations result \cite[Theorem~2, \S
    XVI.7]{feller71:_introd_probab_theor_its_applic,rubin65:_probab}.

@@

      \frac{1 - F_{n}(u)}{1 - \Phi(u)} = \Bigl[1 + (C\tfrac{u^{3}}{\sqrt{n}}) + O(\tfrac{u^{6}}{n}) \Bigr]

@@

    for some constant $C$. Letting $u_n = a_n + b_n x$ in

@@

     F_n(u_n) &= 1 - (1 - \Phi(u_n))(1 + C \tfrac{u_n^{3}}{\sqrt{n}} +
     O(\tfrac{u_n^{6}}{n})) \\
     &= \Phi(u_n) + (1 - \Phi(u_n))(C \tfrac{u_n^{3}}{\sqrt{n}} +
     O(\tfrac{u_n^6}{n})) \\
     &= \Phi(u_n) + O(\tfrac{1}{u_n n^{1- \delta}})(C \tfrac{u_n^{3}}{\sqrt{n}} +
     O(\tfrac{u_n^6}{n})) \\
     &= \Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})

@@

    for some sufficiently small $\delta > 0$. We therefore have

@@

      \mathbb{P}(\max_{v \in [n]} \zeta(v) \leq u_n) &= (F_n(u_n))^{n} \\
      &= \Bigl[\Phi(u_n) + O(\tfrac{u_n^{5}}{n^{3/2 - \delta}})\Bigr]^{n} \\
      &= (\Phi(u_n))^{n} + O(\tfrac{u_n^{5}}{n^{1/2 - \delta}}) \\

@@

    Eq.~\eqref{eq:22} is established and we obtain the limiting Gumbel distribution for

@@

  For ease of exposition we drop the index $t^{*}$ from our discussion. Let

@@

    \limsup\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \leq \lim

@@

  \liminf\,\, \mathbb{P}( \Upsilon(G) \geq a_{n,m} ) \geq \lim \mathbb{P}(

@@

    \frac{P_2}{n} & \leq \sum_{e + f \geq
        d_{n,m}}{\mathbb{P}( Y(v) - h(v) \geq
      \vartheta_{n}, M(v) = e, W(v) = f) p_{e,f}}

@@

  &=  \sum_{e + f \geq d_{n,m}}{\mathbb{P}(
    \tfrac{Y(v) - h(v)}{\mathrm{Var}[Y(v)]^{1/2}} \geq
    \tfrac{\vartheta_n}{\mathrm{Var}[Y(v)]^{1/2}}, M(v) = e, W(v) = f) p_{e,f}} \\
    &\leq \sum_{e + f \geq d_{n,m}} (1 + o(1))
    \mathbb{P}(Z \geq \Theta(\log{n})) p_{e,f} = o(n^{-1})

@@

$\{v \in [m] \cap (\mathfrak{E} \cap\mathfrak{F})\}$ and $\{v \in [m]

@@

  We now show that $\mathbb{P}( \cup_{v

@@

      N_{\kappa}) = o(1)$. We note that $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
      N_{\kappa})$ can be rewritten as
        \sum_{e + f \geq N_{\kappa}}{\mathbb{P}(Y(v) \leq a_{n,m}, M(v) = e, W(v) =
          f)}p_{e,f}
We now split the indices set $e + f \geq N_{\kappa}$ in
Eq.~\eqref{eq:24} into three parts $S_1$, $S_2$ and $S_3$, namely
  \label{eq:32}
    S_1 = \{ \{e,f\}\colon e \geq
        \mu_E + \sigma_E \log{m}\} \\
    S_2 = \{ \{e,f\} \colon  e \leq
        \mu_E + \sigma_E \log{m},e + f \leq
        N_\kappa + \varphi(n)\} \\
    S_3 = \{ \{e,f\} \colon e \leq \mu_E + \sigma_E \log{m}, e + f \geq
        N_\kappa + \varphi(n)\}
where $\varphi(n) = \Theta(n^{1/2 - a})$ for some $a > 0$. We can then
show that $m\mathbb{P}(M(v) = e,
W(v) =f, \{e,f\} \in S_1) = o(1)$ by applying a concentration
inequality. Similarly, $e + f \geq N_{\kappa}$ and $e \leq \mu_{E}
+ \sigma_{E} \log{m}$ implies that
  \label{eq:33}
  f \geq \mu_{F} + (z_{m} - o(1)) \sigma_F 
and once again, by a concentration inequality, we can show that m
$\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for
$S_3$, from the fact that $e + f \geq N_{\kappa} + \varphi(n)$, we have the bound
    a_{n,m} - h(v) &\leq (C_{11} p_{11} - C_{10} p_{10})[m \sigma_E
    \log{m} + \tbinom{\log{m}}{2}] \\ &- C_{00}p_{00} N_\kappa \varphi(n)
  As $\mathrm{Var}[Y(v)] = \Theta(N_\kappa)$ for $\{M(v), W(v)\} \in
  S_3$, we have
    \label{eq:39}
      p_{S_3} &= \sum_{\{e,f\} \in S_3} \mathbb{P}( Y(v) < a_{n,m}) p_{e,f} 
      \\ &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl(\tfrac{Y(v) - h(v))}{\mathrm{Var}[Y(v)]^{1/2}} \leq \tfrac{a_{n,m} -
      h(v)}{\mathrm{Var}[Y(v)]^{1/2}}\Bigr)p_{e,f} \\
    &\leq \sum_{\{e,f\} \in S_3} \mathbb{P}\Bigl[Z \leq
    O\bigl(\tfrac{m^{3/2} \log m}{N_{\kappa}} - \varphi(n)\bigr)\Bigr] p_{e,f}
  We now set $a = \tfrac{1}{2(k+1)}$. Then for $m =
  O(n^{k/(k+1)})$ and $\varphi(n) = O(n^{1/2 - a})$ we have
    \label{eq:41}
    \tfrac{m^{3/2} \log m}{N_\kappa} - \varphi(n) =
    -O(n^{k/2(k+1))})
  which then implies
    p_{S_3} \leq \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
    - O(n^{k/2(k+1)}\Bigr] p_{e,f} = o(1)
  Thus $\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
      N_{\kappa}) \rightarrow 0$ as desired.

@@

\end{proof}
\bibliography{ssp2011}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:
